Tracing the Stellar Halos of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using Hyper Suprime-Cam

### 2017-06-29 draft/paper1_rachel.tex
Edit 1-D profile selection 2

%% ------------------------------------------------------------------------------------ %% 
    \begin{figure*}
        \centering 
        \includegraphics[width=\textwidth]{fig/redbcg_ellipse_example}
        \caption{
            Left: example of the 1-D surface brightness and ellipticity profile 
            for a massive galaxy at $z=0.23$ in the $i$-band using \texttt{Ellipse}. 
            In this work, we always show the radial profile using a $R^{1/4}$ scaling 
            on the x-axis. \rachel{So should the units be kpc$^{1/4}$?}
            By using this scale, the de Vaucouleurs profile will appear as a straight 
            line on this figure.  
            We also plot the relative brightness profile of the PSF model normalized 
            at the central surface brightness of the galaxy to highlight the region 
            most strongly affected by seeing.
            The grey shaded region highlights the region ($r<6$ kpc) that is equivalent 
            to twice the size of the half-width of a 1\asec{} seeing at $z\sim 0.5$.
            It is a very conservative estimate of the region that we can not reliable 
            extract 1-D profile due to the smearing effect of seeing.
            On the top panel, the dashed line shows the ellipticity used for the final 
            isophote. 
            Right: the three color image of this galaxy with isophotes 
            extracted by \texttt{Ellipse}. 
            The thick dotted line highlights the isophote with 
            $\mu_{i}{\sim} 28.5$~\sb.
            }
        \label{fig:ellipse}
    \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    We test our procedure using different mask sizes, different \texttt{Ellipse} 
    parameters, and with or without our background correction. 
    Based on these tests, we find that our 1-D surface brightness profiles are reliable 
    up to surfaces brightness levels of $i{\sim}28.5$ \sb. 
    Beyond that, some of our profiles shows signs of truncation and/or large 
    fluctuations which are due to either the uncertainty in the background 
    subtraction or the unmasked flux from other objects.
    We choose to limit our study to surface brightness levels up to ${\sim} 28.5$ \sb. 
    This is a conservative choice but already enables us to measure light profiles 
    out to $100$ kpc on a galaxy-by-galaxy basis (no stacking). 
    For more technical details of the \texttt{Ellipse} procedure, please see 
    Appendix~\ref{app:ellipse}.

@@

    For physical (e.g.\ late-stage major merger) and nuisance (e.g.\ nearby foreground 
    galaxy or bright star) reasons, we cannot extract reliable 1-D profiles for a small 
    fraction of massive galaxies because they are heavily masked out. 
    This is an intrinsic limitation of the 1-D method, and it removes ${\sim}10$\% of 
    the sample.
    %It affects $18/164$ of the \rbcg{} sample, and a smaller fraction of the 
    %\nbcg{} sample. 
    It is worth noting that this excludes most massive galaxies undergoing major mergers.

    Given our exquisite profiles that extend to 100 kpc, the definition and meaning 
    of ``total'' magnitude (and stellar mass) becomes nuanced.
    With the help of the \m2l{} estimated in the next section (\S \ref{sec:mstar}), 
    we integrate the profile to a range of radii, and estimate the stellar mass 
    within these different apertures.  \rachel{You should at least clarify whether it's a radius-dependent \m2l{} here or not, so readers know whether both luminosity and \m2l{} depend on radius, or just luminosity.}
    Motivated by the two-phase scenario, we will consider two benchmark physical 
    apertures throughout this work:

@@

        \item \textbf{The \mstar{} within the inner 10 kpc} 
            (hereafter noted \minn{}). 
            According to the two-phase scenario, the \textit{in situ} star-formation phase quickly builds up the inner, dense core of massive ETGs.  
            Based on recent observation (e.g.~\citealt{vanDokkum2010}) and 
            simulations (e.g. \citealt{RodriguezGomez2016}), the \textit{in situ} 
            component dominates the \mstar{} within one effective radius 
            ($R_{\mathrm{e}}$, or 5-10 kpc) of $z{\sim}0$ massive ETGs.
            We therefore use \minn{} as proxy for the mass forged during the 
            \textit{in situ} phase. 
            Given the quality of the HSC data, we can reliably measure \minn{} over 
            our redshift range ($1.0^{\arcsec}$ in radius equals 4.4 and 6.1 kpc 
            at redshifts 0.3 and 0.5 respectively).  
\rachel{Earlier you said you do not measure the profiles on the very smallest scales, below 3-5 kpc, so how are scales in that range handled when measuring \mstar{} within 10 kpc?}
It is worth noting that, at the very high-\mstar{} end, accreted stars may make a significant contribution to the mass within 10 kpc 
            (e.g. \citealt{RodriguezGomez2016}). We will further discuss the justification of this assumption in 
            \ref{ssec:twophase}.

        \item \textbf{The stellar mass within 100 kpc} 
            (hereafter noted \mtot{}). 
            For our galaxy sample, a 100 kpc aperture corresponds to 5-10 
            $\times R_{\mathrm{e}}$. 
            We show in section \ref{ssec:mtotal} that most of the \mstar{} for 
            these ETGs can be captured by a 100 kpc radius and that \mtot{} is 
            a good proxy for the ``total'' \mstar{}. 
            Although not perfect, we argue that our measurements of \mtot{} (which are 
            actually measuring the light directly out to 100 kpc) are a better tracer 
            of total \mstar{} than model-dependent results from shallower data 
            (such as SDSS) which rely on extrapolating the light profiles of galaxies 
            out to large radii.

>>>>

%% ------------------------------------------------------------------------------------ %% 
    \begin{figure*}
        \centering 
        \includegraphics[width=\textwidth]{fig/redbcg_ellipse_example}
        \caption{
            Left: example of the 1-D surface brightness and ellipticity profile 
            for a massive galaxy at $z=0.23$ in the $i$-band using \texttt{Ellipse}. 
            In this work, we always show the radial profile using a $R^{1/4}$ scaling 
            on the x-axis.
            By using this scale, the de Vaucouleurs profile will appear as a straight 
            line on this figure.  
            We also plot the relative brightness profile of the PSF model normalized 
            at the central surface brightness of the galaxy to highlight the region 
            most strongly affected by seeing.
            The grey shaded region highlights the region ($r<6$ kpc) that is equivalent 
            to twice the size of the half-width of a 1\asec{} seeing at $z\sim 0.5$.
            It is a very conservative estimate of the region that we can not reliable 
            extract 1-D profile due to the smearing effect of seeing.
            On the top panel, the dashed line shows the ellipticity used for the final 
            isophote. 
            Right: the three color image of this galaxy with isophotes 
            extracted by \texttt{Ellipse}. 
            The thick dotted line highlights the isophote with 
            $\mu_{i}{\sim} 28.5$~\sb.
            }
        \label{fig:ellipse}
    \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    We test our procedure using different mask sizes, different \texttt{Ellipse} 
    parameters, and with or without our background correction. 
    Based on these tests, we find that our 1-D surface brightness profiles are reliable 
    up to surfaces brightness levels of $i{\sim}28.5$ \sb. 
    Beyond that, some of our profiles shows signs of truncation and/or large 
    fluctuations which are due to either the uncertainty in the background 
    subtraction or the unmasked flux from other objects.
    We choose to limit our study to surface brightness levels up to ${\sim} 28.5$ \sb. 
    This is a conservative choice but already åenables us to measure light profiles 
    out to $100$ kpc on a galaxy-by-galaxy basis (no stacking). 
    For more technical details of the \texttt{Ellipse} procedure, please see 
    Appendix~\ref{app:ellipse}.

@@

    For physical (e.g.\ late-stage major merger) and nuisance (e.g.\ nearby foreground 
    galaxy or bright star) reasons, we cannot extract reliable 1-D profiles for a small 
    fraction of massive galaxies because they are heavily masked out. 
    This is an intrinsic limitation of the 1-D method, and it removes ${\sim}10$\% of 
    the sample.
    %It affects $18/164$ of the \rbcg{} sample, and a smaller fraction of the 
    %\nbcg{} sample. 
    We visually examine the 3-color images of randomly selected galaxies with failed 
    1-D profile.  
    Most of them are relative small galaxies that are severly contaminated by nearby 
    objects, and will not affect the results of this work.  
    Meanwhile, tt is worth noting that this does exclude most major merging systems 
    among massive galaxies.

    Given our exquisite profiles that extend to 100 kpc, the definition and meaning 
    of ``total'' magnitude (and stellar mass) becomes nuanced.
    With the help of the average \m2l{} estimated in the next section 
    (\S \ref{sec:mstar}), we integrate the profile to a range of radii, and estimate 
    the stellar mass within these different apertures.  
    Motivated by the two-phase scenario, we will consider two benchmark physical 
    apertures throughout this work:

@@

        \item \textbf{The \mstar{} within the inner 10 kpc} 
            (hereafter noted \minn{}). 
            According to the two-phase scenario, the \textit{in situ} star-formation 
            phase quickly builds up the inner, dense core of massive ETGs.  
            Based on recent observation (e.g.~\citealt{vanDokkum2010}) and 
            simulations (e.g. \citealt{RodriguezGomez2016}), the \textit{in situ} 
            component dominates the \mstar{} within one effective radius 
            ($R_{\mathrm{e}}$, or 5-10 kpc) of $z{\sim}0$ massive ETGs.
            We therefore use \minn{} as proxy for the mass forged during the 
            \textit{in situ} phase. 
            Given the quality of the HSC data, we can reliably measure \minn{} over 
            our redshift range ($1.0^{\arcsec}$ in radius equals 4.4 and 6.1 kpc 
            at redshifts 0.3 and 0.5 respectively).  
            It is worth noting that, at the very high-\mstar{} end, accreted stars 
            may make a significant contribution to the mass within 10 kpc 
            (e.g. \citealt{RodriguezGomez2016}). 
            We will further discuss the justification of this assumption in 
            \ref{ssec:twophase}.

        \item \textbf{The stellar mass within 100 kpc} 
            (hereafter noted \mtot{}). 
            For our galaxy sample, a 100 kpc aperture corresponds to 5-10 
            $\times R_{\mathrm{e}}$. 
            We show in Section \ref{ssec:mtotal} that most of the \mstar{} for 
            these ETGs can be captured by a 100 kpc radius and that \mtot{} is 
            a good proxy for the ``total'' \mstar{}. 
            Although not perfect, we argue that our measurements of \mtot{} (which are 
            actually measuring the light directly out to 100 kpc) are a better tracer 
            of total \mstar{} than model-dependent results from shallower data 
            (such as SDSS) which rely on extrapolating the light profiles of galaxies 
            out to large radii.
